\section{Background}
\subsection{OSPF}

\subsection{BGP}
BGP is a path-vector routing protocol that connects 
different autonomous systems (ASes), where each AS
comprises of one or more routers (typically managed
by a single entity). 
\minisection{eBGP}
\\
\minisection{iBGP}

\subsection{BGP Best Path Selection Algorithm}
A BGP router receives multiple paths to the destination: (1)
external routes from border routers of neighbouring domains using
eBGP, and (2) routes learned by other BGP routers 
of the domain which are advertised using iBGP. 
BGP decides the best path to install in the 
forwarding table based on different metrics like local preferences,
AS path lengths and type of routes~\cite{bgp}. BGP uses the
rules specified in \Cref{alg:bgppathrules}\footnote{
For ease of presentation, we list an abridged ruleset; 
the synthesized configurations will only use these rules 
for routing.  
} 
in decreasing order of preference to select the best path
from the received announcements. If all paths result in a tie
at $i^{th}$ rule, then the $i+1^{th}$ rule is considered.
\begin{algorithm}
	\begin{footnotesize}
		\caption{BGP Best Path Selection Rules}
		\label{alg:bgppathrules}
		\begin{algorithmic}[1]
				\State{Prefer the path with the highest \emph{local preference}.}
				\State{ Prefer the path with the smallest AS Path length. }
				\State{Prefer the path with the lowest \emph{multi-exit discriminator} (MED).}
				\State{Prefer eBGP over iBGP paths.}
				\State{Prefer the route that comes from the BGP router with the lowest \emph{router ID}.}
		\end{algorithmic}
	\end{footnotesize}
\end{algorithm}


